Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-24 paper.qmd
Added another parameter choice with tSNE

```{r}
#| label: read-two-curvy-clust-nldr
# Read a variety of different NLDR representations of two_non_linear_diff_shaped_close_clusters
# and plot them on same aspect ratio
tsne_two_curvy <- read_rds("data/two_nonlinear/two_non_linear_diff_shaped_close_clusters_tsne_perplexity_30.rds")

>>>>

```{r}
#| label: read-two-curvy-clust-nldr
# Read a variety of different NLDR representations of two_non_linear_diff_shaped_close_clusters
# and plot them on same aspect ratio
tsne_two_curvy <- read_rds("data/two_nonlinear/two_non_linear_diff_shaped_close_clusters_tsne_perplexity_47.rds")
